---
title: '#XRP Twitter Network Analysis'
author: "Joseph Cook"
date: "October 22, 2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, include = FALSE)
```

```{r libraries, include=FALSE}
library(vosonSML)
library(sna)
library(igraph)
library(network)
library(tidyverse)
```

# Data Collection

```{r twitter_auth}
# keys <- list(appName = "XRP", 
#              apiKey = Sys.getenv("twitter_api_key"), 
#              apiSecret = Sys.getenv("twitter_api_secret"), 
#              accessToken = Sys.getenv("twitter_access_token"),
#              accessTokenSecret = Sys.getenv("twitter_access_secret"))
# 
# twitterAuth <- Authenticate("twitter", appName = keys$appName, apiKey = keys$apiKey, 
#                             apiSecret = keys$apiSecret, accessToken = keys$accessToken,
#                             accessTokenSecret = keys$accessTokenSecret)

#twitterAuth <- readRDS(".twitter_auth")
```

```{r twitter_search}
#twittersearchTerm <- c('#XRP')

# twitterData <- twitterAuth %>%
#   Collect(searchTerm = twittersearchTerm, searchType = "recent", numTweets = 1100, 
#           includeRetweets = TRUE , retryOnRateLimit = TRUE, writeToFile = FALSE, 
#           verbose = TRUE)

# View(twitterData)
load("xrp_twitter_network.Rdata")
```

```{r actor_network}
# actorNetwork <- twitterData %>% Create("actor")
# actorGraph <- actorNetwork$graph
```

```{r clean_edges}
edge_cleanup <- function(graph = actorGraph){
  library(igraph)
  df <- get.data.frame(actorGraph)
  names_list <- data.frame('name' = as.character(V(actorGraph)$name),
                           'label' = as.character(V(actorGraph)$label))
  df$from <- sapply(df$from, function(x) names_list$label[match(x,names_list$name)] %>% as.character())
  df$to <- sapply(df$to, function(x) names_list$label[match(x,names_list$name)] %>% as.character())
  nodes <- data.frame(sort(unique(c(df$from,df$to))))
  links <- df[,c('from','to')]
  net <- graph.data.frame(links, nodes, directed=T)
  E(net)$weight <- 1
  net <- igraph::simplify(net,edge.attr.comb="sum")
  return(net)
}

# actorGraph <- edge_cleanup()
```

```{r basic_network_stats}
# check if the network is directed or undirected
is.directed(actorGraph)

########################
# Check the criterion
########################
# check the size of the network
vcount(actorGraph) ## the number of nodes/actors/users
ecount(actorGraph) ## the number of edges

possible_links <- vcount(actorGraph) * (vcount(actorGraph) - 1)

# calculate the density of the network
graph.density(actorGraph)
```

## XRP Network

XRP is a crypto-asset native to the XRP ledger. It is infamously tied to the company, Ripple, who owns a majority of XRP at the moment even though the ledger is open-source technology. Ripple and the larger XRP community have been making great strides at positioning XRP as the ultimate "bridge currency" for all other two-pair currency exchanges. Their vision is the "Internet of Value" where we will be able to send money/value back and forth similar to the way we share data on the internet. I am intrigued by the future of XRP and the XRP ledger, thus I wanted to analyze the #XRP hashtag to see if I could learn about the social network on Twitter.

I chose the #XRP hashtag as I have seen it more often than any other related hashtag. While this is already a nascent industry with only a small comparative following I felt it was important to use the broadest, most well recognized hashtag. Also, whenever there are arguments about the advantages of XRP versus, say Bitcoin (BTC), those tweets usually involve the #XRP hashtag, so I am curious to see if I will capture any of that.

Mostly, I am hoping to see if I can identify the major leaders of the "XRP Army" (a nickname for the XRP fanbase), as well as the most dedicated soldiers. I imagine that leaders will have some form of high degree-centrality, and top soliders/followers will have a high betweeness measure. Also, I am interested in the overall composition of the network and how disjointed or connected it is.

## Basic Network Statistics

The graph is `r if(is.directed(actorGraph)) paste0("directed") else paste0("undirected")`.  
There are `r vcount(actorGraph)` nodes and `r ecount(actorGraph)` edges in this network.  
There are 683,102 possible links in the network.  
The density of this network is `r graph.density(actorGraph)`.  

## Data Considerations

If I wanted to look at a broader crypto network, I would want to use the #crypto hashtag. If I wanted to look at the other side of most crypto arguments (compared to the XRP Army), I would want to look at the #BTC (bitcoin) hashtag. By using the #XRP hashtag, I am boxing myself into somewhat of a narrow network, most-likely with similar nodes. Given the purpose of this analysis, this is ok.

# Network Visualization

```{r load_network_data}
# load("xrp_twitter_network.Rdata")
```

## Full Network

### Force-directed Layout Algorithm

```{r full_network_graph, include = TRUE}
# Plot a graph
actorGraph %>% 
  plot(.,
       layout = layout_with_fr(.),
       edge.arrow.size = .3,
       vertex.size = 7,
       vertex.color = 'red',
       vertex.label = NA, ## uncomment here if you don't want to display labels
       vertex.label.cex = .5,
       vertex.label.color = 'black')
```

```{r full_components}
# Calculate the number of components in the graph
comp <- components(actorGraph)
comp$csize
comp$no
```

The first observation I see is the giant component to the lower left of the graph with many smaller (and in many cases isolated) components in a moon shape around the top right of the graph. 

Digging deeper, there are `r comp$no` different components (sizes below). The giant component contains `r max(comp$csize)` nodes, while `r length(which(comp$csize == 1))` of the components are isolated and `r length(which(comp$csize <= 3))` of the components contain 3 or less nodes.

`r comp$csize`

Even within the giant component though, there seems to be a few saturated groups similar to the 3 components of 12-17 nodes. My hypothesis is that there are roughly ~10 main conversations going on, likely started by major movers in the XRP space, and these conversations are then linked by a few nodes who are active across the whole space (high betweenness).


## Giant Component

### Force-directed Layout Algorithm

```{r giant_graph, include=TRUE}
# Take out a giant component from the graph
giantGraph <- actorGraph %>% 
  induced.subgraph(., which(comp$membership == which.max(comp$csize)))
#vcount(giantGraph) ## the number of nodes/actors/users
#ecount(giantGraph) ## the number of edges

# Plot a graph of giant component. (.) in layout gets the last data
giantGraph %>% 
  plot(.,
       layout = layout_with_fr(.),
       edge.arrow.size = .3,
       vertex.size = 4,
       vertex.color = 'red',
       vertex.label = NA,
       vertex.label.cex = .5,
       vertex.label.color = 'black')
```

After separating out the giant component from the full network I was able to better visualize my hypothesis of multiple main conversations/head nodes. From this visualization I am able to account for ~10 "groups" centered around a single node. 

This also gives better insight into the nodes on the periphery. There are multiple "spikes" coming from out of the center of the giant component. Interestingly, the arrows seem to be pointing outward as you move out for the most part. This seems to support my other hypthesis that there are some nodes with high betweeness that participate not only in the main conversations, but even connect and interact with non-influential nodes, thereby connecting them to the giant component.

### Simulated Annealing Algorithm + Node Weights by Degree

```{r giant_graph_2, include=TRUE}
# Experiment with other layouts by replacing with your choice of layout, then running a plot function above.
# layout = layout_with_...(.)
# For that, you can pick one of the options below.
# layout_with_dh(.) # Davidson and Harel
# layout_with_drl(.) # Force-directed
# layout_with_kk(.) # Spring

# You can play with the vertex sizes and/or edge sizes to get a better vizualization for the graphs above

V(giantGraph)$vertex_degree <-  degree(giantGraph)

giantGraph %>%
  plot(.,
       layout = layout_with_dh(.),
       edge.arrow.size = .1,
       edge.curved = TRUE,
       vertex.size = V(giantGraph)$vertex_degree,
       vertex.color = grDevices::adjustcolor("#63B8FF", alpha=0.5),
       vertex.label = NA)

```

I used the simulated annealing layout algorithm (layout_with_dh) for this visualization because it successfuly separating out the nodes with high degree in a way that I could visualize them easier. I also sized each node by it's degree, which allows us to see clearly that there are ~10 high-degree nodes in the giant component of this network. Also, there are ~50 nodes that have a degree high enough to substantiate on the visualization. Again, this visualization confirms my hypothesis of a few major nodes where the activities in the network are centered, with a slightly larger number of nodes acting as connectors for the network.

# Individual Network Properties

```{r igraph_to_sna}
sna_graph <- igraph::get.adjacency(giantGraph, sparse=FALSE) %>% network::as.network.matrix()
detach('package:igraph')
```

```{r compute_centralities}
# Compute centralities based on 'network' package
# Calculate in-degree centrality
degree(sna_graph, cmode = 'indegree')
# Store the information
centralities <- data.frame('node_name' = as.character(network.vertex.names(sna_graph)),
                           'in_degree' = degree(sna_graph, cmode = 'indegree'))

# Calculate out-degree centrality and store it in the data.frame called 'centralities'
centralities$out_degree <- degree(sna_graph, cmode = 'outdegree')

# Calculate betweenness centrality and store it in the data.frame called 'centralities'
centralities$betweenness <- betweenness(sna_graph)

# Calculate closeness centrality and store it in the data.frame called 'centralities'
centralities$incloseness <- igraph::closeness(giantGraph, mode = 'in')
centralities$outcloseness <- igraph::closeness(giantGraph, mode = 'out')

# Calculate eigenvector centrality and store it in the data.frame called 'centralities'
centralities$eigen <- evcent(sna_graph)

# Calculate Burt's network constraint and store it in the data.frame called 'centralities'
# using 'igraph' because 'sna' doesn't have the function
centralities$netconstraint <- igraph::constraint(giantGraph)

# Calculate authority and store it in the data.frame called 'centralities'
# using 'igraph' because 'sna' doesn't have the function
# 'igraph::' allows calling for any igraph function without loading the package
centralities$authority <- igraph::authority_score(giantGraph, scale = TRUE)$`vector`

# Calculate hub and store it in the data.frame called 'centralities'
# using 'igraph' because 'sna' doesn't have the function
centralities$hub <- igraph::hub_score(giantGraph, scale = TRUE)$`vector`

#View(centralities)
```

## Target Diagram - Betweenness

```{r target_diagram, include = TRUE}
# Produce a target diagram, centering by one of your choice of centralities (e.g., betweenness)
# WARNING - below might take some time to produce it 
# if you're running other tasks on your computer, make sure that your CPU has some space to run this plot
sna::gplot.target(sna_graph, centralities$betweenness,
                  displaylabels = FALSE, ## if you don't want to see labels, replace TRUE with FALSE
                  label.cex=.5,
                  main="Betweenness",
                  # circ.lab = TRUE,
                  circ.col="skyblue",
                  usearrows = TRUE,
                  # vertex.col=c("blue", rep("red", 32), "yellow"),
                  edge.col="darkgray")

```

## Centrality Ranks

```{r create_node_table, include=TRUE}
# For creating the table in part III you can use the following, replace eigen with other centrality measures that you want

ranks <- data.frame("Rank" = 1:10)

ranks <- ranks %>% 
  mutate("In-degree" = centralities %>% arrange(desc(in_degree)) %>% head(10) %>% mutate("In-degree" = paste0(node_name, " (", round(in_degree,3), ")")) %>% pull("In-degree"),
         "Out-degree" = centralities %>% arrange(desc(out_degree)) %>% head(10) %>% mutate("Out-degree" = paste0(node_name, " (", round(out_degree,3), ")")) %>% pull("Out-degree"),
         "Betweenness" = centralities %>% arrange(desc(betweenness)) %>% head(10) %>% mutate("Betweenness" = paste0(node_name, " (", round(betweenness,3), ")")) %>% pull("Betweenness"),
         "In-closeness" = centralities %>% arrange(desc(incloseness)) %>% head(10) %>% mutate("In-closeness" = paste0(node_name, " (", round(incloseness,8), ")")) %>% pull("In-closeness"),
         "Out-closeness" = centralities %>% arrange(desc(outcloseness)) %>% head(10) %>% mutate("Out-closeness" = paste0(node_name, " (", round(outcloseness,8), ")")) %>% pull("Out-closeness"),
         "Eigen" = centralities %>% arrange(desc(eigen)) %>% head(10) %>% mutate("Eigen" = paste0(node_name, " (", round(eigen,3), ")")) %>% pull("Eigen"),
         "Net-constraint" = centralities %>% arrange(desc(netconstraint)) %>% head(10) %>% mutate("Net-constraint" = paste0(node_name, " (", round(netconstraint,3), ")")) %>% pull("Net-constraint"),
         "Authority" = centralities %>% arrange(desc(authority)) %>% head(10) %>% mutate("Authority" = paste0(node_name, " (", round(authority,3), ")")) %>% pull("Authority"),
         "Hub" = centralities %>% arrange(desc(hub)) %>% head(10) %>% mutate("Hub" = paste0(node_name, " (", round(hub,3), ")")) %>% pull("Hub"))

knitr::kable(ranks[,c(1:5)])
```

```{r node_table_2, include=TRUE}
knitr::kable(ranks[,c(1,6:9)])
```

```{r node_table_3, include=TRUE}
knitr::kable(ranks[,c(1,10)])
```

## Discusson on Individual Network Properties

##### Centrality Measures

**In-degree:** The number of directional links to the node. In this scenario, it would be the number of nodes who replied or retweeted the node. A high in-degree signifies a central figure in the XRP community because the node is trusted enough to be responded to and retweeted.    
**Out-degree:**  The number of directional links to other nodes. In this scenario, it would be the number of people this node replied to or retweeted. A high out-degree singals a figure who is active in the space more broadly and participates in more conversations.  
**Betweenness:** The number of geodesic distances that pass through a node. A high betweenness score means the figure is a bridge between main conversations on Twitter. If you want to follow more conversations, follow these nodes.  
**In-closeness:** Closeness measures how close a node is to the rest of the nodes in the network. Specifically, in-closeness corresponds to the ease of which a node can spread information anywhere in the network. In this analysis, a high in-closeness would be a figure who is at the center of the network and has been replied or retweeted in multiple different conversations.  
**Out-closeness:** Out-closeness is the opposite, measuring how easy it is for a node to get information from the outside network. In this analysis, this would be a node that is plugged in to many different nodes in many different conversations.   
**Eigenvector:** A function of a node's neighbors' centralities. A node in this scenario that has a high eigenvector centrality would be someone who is closely related to multiple high-degree nodes, and has some moderate level of degree themselves. These nodes are well integrated into the community.  
**Burt's network constraint:** A measure of the extent to which a node's connections are circular, or connected with each other. Nodes with high constraint have difficulty getting access to new information because of their lack of outside connections. In this analysis, this would be a person that is only involved in one or two conversations and is unaware of outside activity.   
**Authorities & Hubs:** Authorities contain useful information, and Hubs indicate where the autorities can be found. These two metrics are cacluated together. The authority score is proportional to the sum of hub scores pointing to it, while the hub score is proportional to the sum of authority scores it points to. In the XRP network, authorities should be the main sources of information, while hubs should be the main relayers of information.    

##### Centrality in the XRP Network

Looking across the centrality measures for the XRP Network, there are a few that don't seem to be great measures due to the sparse density of the network as a whole: in-closeness, out-closeness, net-constraint, and potentially authorities and hubs. It seems like in-degree, out-degree, betweenness, and eigenvector centrality are the richest measures of centality for this network.

Kevin_Cage_ appears as the third-highest in-degree centrality. This node also appears second-highest in betweenness, and seventh in eigenvector centrality. Across all metrics, this appears to be of the the most central nodes. DigitalNomadInv is ninth in in-degree and first in both out-degree and betweenness. I would characterize Kevin_Cage_ as a highly influential node, and DigitalNomadInv as the highest broker in the network - connecting multiple players throughout. 


# Global Network

```{r detach_packages}
detach('package:sna', unload = TRUE)
detach('package:network', unload = TRUE)
library(igraph)
```

## K-cores

```{r kcores}
kcore <- giantGraph %>% graph.coreness(.)
kcore

V(giantGraph)$vertex_degree <-  degree(giantGraph)

table(kcore)
```

```{r kcores_viz, include = TRUE}
giantGraph %>%
  plot(.,
       layout = layout_with_dh(.),
       edge.arrow.size = .1,
       edge.curved = TRUE,
       vertex.size = V(giantGraph)$vertex_degree,
       vertex.color = adjustcolor(graph.coreness(.), alpha.f = .3),
       vertex.label = NA,
       mark.groups = by(seq_along(graph.coreness(.)), graph.coreness(.), invisible),
       mark.shape = 1/4,
       mark.col = rainbow(length(unique(graph.coreness(.))),alpha = .1),
       mark.border = NA)
```

A k-core is the max group of nodes that are all directly connected to "k" other nodes of the network. There are 3 cores in this network - sizes `r table(kcore)[1]`, `r table(kcore)[2]`, and `r table(kcore)[3]`, respectively. This shows that there are a lot of minor participants that are hopping into one conversation, making just one reply or retweet.

I believe the k-core decomposition makes sense for this network. Only looking at 1000 tweets, you would only expect a handful of nodes to be more than just passerbys. The ~50 nodes in the 3-core are likely bigger activists or more passionate about XRP as a whole.

## Communities, Modularity, and Clusters

```{r communities}
# Community detection: Plot the number of clusters in the graph and their size
# there are also other algorithms for this you may want to explore
# below is using Newman-Girvan Algorithm (2003)
# if communities do not make sense to you, replace with your choice
# e.g., cluster_infomap, cluster_walktrap etc.
cluster <- giantGraph %>% cluster_edge_betweenness()
cluster

# modularity measure
modularity <- modularity(cluster)

# Find the number of clusters
cluster_membership <- membership(cluster)   # affiliation list
num_clusters <- length(cluster) # number of clusters

# Find the size the each cluster 
# Note that communities with one node are isolates, or have only a single tie
cluster_sizes <- sizes(cluster) 
```

```{r communities_viz, include = TRUE}
# Visualize clusters - that puts colored blobs around the nodes in the same community.
# You may want to remove vertex.label=NA to figure out what terms are clustered.
cluster %>% plot(.,giantGraph,
                 # layout = layout_with_gem(.),
                 layout = layout_nicely(giantGraph),
                 edge.arrow.size = .3,
                 edge.color = "lightgrey",
                 edge.width = .2,
                 vertex.size = V(giantGraph)$vertex_degree,
                 vertex.color = adjustcolor(membership(.), alpha.f = .1),
                 vertex.label = NA,
                 mark.groups = by(seq_along(membership(.)), membership(.), invisible),
                 mark.shape = 1/4,
                 mark.col = rainbow(length(.),alpha = .1),
                 mark.border = NA
)
```

I chose to use the edge betweenness community detection algorithm because it is supposed to be ideal for communities which are densely connected to themselves but sparsely connected to others. This made the most sense to me given the network is Twitter activity. where specific conversations are had in threads (dense connection).

`r num_clusters` communities were created. As mentioned, I think a community of nodes represents threads that a group of nodes gets involved in. There is not a high amount of crossover between threads as denoted by the lack of density in the network.

The modularity of the network is `r modularity`. Modularity is on a spectrum from -1 to 1. This is on the higher end, although not super high. Modularity suggests dense connections within modules and sparse connections between modules. My hypothesis is that while there are sparse connections between modules, the connections within a module are next extremely dense, as a node does not often reply to all other nodes in a given thread on Twitter, just one or two.

Now, turning my attention to the cluster visualization, there seems to be a large overlap between one cluster and many others. There are quite a few clusters of low-degree nodes as you move to the periphery of the network, and these are connected to the largest degree nodes by brokers who have a moderate level of degree and, I am assuming, a higher level of betweenness. Nodes in similar clusters seem to have a common broker node - I see this as a result of sub-threads within main threads on Twitter.

## Degree Distributions

##### In-Degree

```{r degree_distributions, include = TRUE}
# Examine the in-degree distribution
giantGraph %>% degree.distribution(.,mode="in") %>% 
  plot(., col = 'black', pch = 19, cex = 1.5,
       main = 'In-degree Distribution',
       ylab = 'Density',
       xlab = 'In-degree')
```

```{r in_degree_loglog, include = TRUE}
# CCDF - Complementary Cumulative Distribution Function
# Plot a log-log plot of in-degree distribution
giantGraph %>% 
  degree.distribution(.,cumulative = TRUE,mode ='in') %>% 
  plot(1:(max(degree(giantGraph,mode='in'))+1),., ## since log doesn't take 0, add 1 to every degree
       log='xy', type = 'l',
       main = 'Log-Log Plot of In-degree',
       ylab = 'CCDF',
       xlab = 'In-degree')
```

```{r in_degree_power_law}
# Fit a power law to the degree distribution
# The output of the power.law.fit() function tells us what the exponent of the power law is ($alpha)
# and the log-likelihood of the parameters used to fit the power law distribution ($logLik)
# Also, it performs a Kolmogov-Smirnov test to test whether the given degree distribution could have
# been drawn from the fitted power law distribution.
# The function thus gives us the test statistic ($KS.stat) and p-vaule ($KS.p) for that test
in_power <- giantGraph %>% 
  degree.distribution(., mode='in') %>%
  power.law.fit(.)
in_power
```

##### Out-Degree

```{r out_degree_distribution, include = TRUE}
# Examine the out-degree distribution
giantGraph %>% degree.distribution(.,mode="out") %>% 
  plot(., col = 'black', pch = 19, cex = 1.5,
       main = 'Out-degree Distribution',
       ylab = 'Density',
       xlab = 'Out-degree')
```

```{r out_degree_loglog, include = TRUE}
# Plot a log-log plot
giantGraph %>% 
  degree.distribution(.,cumulative = TRUE,mode ='out') %>% 
  plot(1:(max(degree(giantGraph,mode='out'))+1), ## since log doesn't take 0, add 1 to every degree
       ., log='xy', type = 'l',
       main = 'Log-Log Plot of Out-degree',
       ylab = 'CCDF',
       xlab = 'Out-degree')
```

```{r out_degree_power_law}
# Fit a power law to the degree distribution
out_power <- giantGraph %>% 
  degree.distribution(., mode='out') %>%
  power.law.fit(.)
out_power
```

##### Degree Summary

**In-Degree C Slope:** `r -in_power$alpha`  
**Out-Degree C Slope:** `r -out_power$alpha`

According to Kolmogov-Smirnov tests, both the in-degree and out-degree distributions follow a power law distribution - meaning that a small portion of the nodes contain a large portion of both the in and out degrees. This make sense given the way that Twitter works. One major influencers makes a post, and then everyone else replies on the thread in a conversation, automatically creating an "in" connection to the influencer. The "rich-get-richer" paradigm is also at play, because the followers of nodes that reply or retweet the influencer get exposed to the influencer, which increases the likelihood that the influencer gets more connections. A lot of power law distributions we see in nature have a power of ~2, so these distributions are a bit less pronounced.

## Small World Properties

```{r small_world}
# Small-world Characteristics
ntrials <- 1000 ## set a value for the repetition
cl.rg <- numeric(ntrials) ## create an estimated value holder for clustering coefficient
apl.rg <- numeric(ntrials) ## create an estimated value holder for average path length
for (i in (1:ntrials)) {
  g.rg <- rewire(giantGraph, keeping_degseq(niter = 100))
  cl.rg[i] <- transitivity(g.rg, type = 'average')
  apl.rg[i] <- average.path.length(g.rg)
}
```

```{r clustering_coef_hist, include = TRUE}
# plot a histogram of simulated values for clustering coefficient + the observed value
hist(cl.rg,
     main = 'Histogram of Clustering Coefficient',
     xlab = 'Clustering Coefficient')
par(xpd = FALSE)
# the line indicates the mean value of clustering coefficient for your network
abline(v = giantGraph %>% transitivity(., type = 'average'), col = 'red', lty = 2)
```

```{r, clustering_coef_test}
# this tests whether the observed value is statistically different from the simulated distribution
t.test(cl.rg, mu=giantGraph %>% transitivity(., type = 'average'),
       alternative = 'less') ##pick either 'less' or 'greater' based on your results
```

```{r avg_path_length_hist, include = TRUE}
# plot a histogram of simulated values for average path length + the observed value
hist(apl.rg,
     main = 'Histogram of Average Path Length',
     xlab = 'Average Path Length')
# the line indicates the mean value of average path length for your network
abline(v = giantGraph %>% average.path.length(), col = 'red', lty = 2)
```

```{r avg_path_length_test}
# this tests whether the observed value is statistically different from the simulated distribution
t.test(apl.rg, mu=giantGraph %>% average.path.length(.),
       alternative = 'greater') ##pick either 'less' or 'greater' based on your results
```


According to the plots and the corresponding t-tests, the observed average clustering coefficient and the observed average path length are not different the randomly simulated data. Small world properties would signal a higher than normal clustering coefficent with a lower than normal average path length - this network does not demonstrate those properties.

# Conclusions

The XRP Network is growing. From a network perspective, there is a lot of growth stil to be had in connecting the ~300 nodes having conversations outside of the main compononent, as well as building greater density into the network as a whole, which would indicate more individual nodes becoming more active participants, thus creating more connections throughout the network. It was interesting to see the power law distributions of both in-degree and out-degree being less than 2. This suggests that there are the highest degree nodes share quite a bit of space in the network.

One of the main goals of this analysis was to try and identify possible leaders in the XRP Army. These findings suggest that Kevin_Cage_, DigitalNomadInv, AlexCobb_, Adam_Kilpatrick, and AndrewNation13 are all worthy of the title "Captain". Looking forward, the key to this network is the nodes with high levels of betweenness, as they act as crucial brokers to fragmented parts of the network. Suprisingly, crypto adoption is largely a social pheonomenon at this point as more use cases get built. In order for the XRP community to continue to grow, these nodes will be responsible for the unifying of the community.


```{r save_image}
save.image('xrp_twitter_network.Rdata')
```

